Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-10-15 demystify.tex
update

If you have an MS then some course work \emph{might be} transferred for course credits, which \emph{might} save some time. But don't count on this.

\begin{commentbox}[Vu:]
    I start my PhD with an MS in CS from a US university.  I found that the MS helped me a lot in research, but not with course work and I had to retake many courses.  In general, don't worry if you don't have an MS. But also don't feel that you wasted your time if you have an MS, as it can help you in research.
  \end{commentbox}

>>>>

If you have an MS then some course work \emph{might be} transferred for course credits, which \emph{might} save some time. But in general don't count finishing earlier just because you have an MS.

\begin{commentbox}[Vu:]
    I start my PhD with an MS in CS from a US university.  I found that the MS helped me in gaining research experience, but I still had to retake courses because I did my MS at a different university.  So in the end, I did not save any time because of the MS.

    In general, don't worry if you don't have an MS. But also don't feel that you wasted your time if you have an MS, as it can help you in research.
  \end{commentbox}
